%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\begin{document}

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}
\textbf{Peer Reviewed Journals}
\begin{enumerate}
\item Shi H., Yan K.K., \textbf{Ding L.}, Qian C., Chi H., Yu J. Network Approaches for Dissecting the Immune System. iScience 23 (8).

\item Silveira A.B., Kasper L.H., Fan Y., Jin H., Wu G., Shaw T.I., Zhu X., Larson J.D., Easton J., Shao Y., Yergeau D.A., Rosencrance C., Boggs K., Rusch M.C., \textbf{Ding L.}, Zhang J., Finkelstein D., Noyes R.M., Russell B.L., Xu B., Broniscer A., Wetmore C., Pounds S.B., Ellison D.W., Zhang J., Baker S.J. H3.3 K27M depletion increases differentiation and extends latency of diffuse intrinsic pontine glioma growth in vivo. Acta Neuropathol. 2019 Apr;137(4):637-655. doi: 10.1007/s00401-019-01975-4.

\item Kohei K., \textbf{Ding L.}, Michael N.E., Stephen V.R., Scott N., John E., Juncheng D., Soheil M., Rhonda E.R., Michael R., Jinghui Z. RNAIndel: discovering somatic coding indels from tumor RNA-Seq data. Bioinformatics, btz753, https://doi.org/10.1093/bioinformatics/btz753.

\item Silveira A.B., Kasper L.H., Fan Y., Jin H., Wu G., Shaw T., Zhu X., Larson J.D., Easton J., Shao Y., Yergeau D.A., Rosencrance C., Boggs K., Rusch M.C., \textbf{Ding L.}, Zhang J., Finkelstein D., Noyes R.M., Russell B.L., Xu B., Broniscer A., Wetmore C., Pounds S.B., Ellison D.W., Zhang J., Baker S.J.. (2019) H3.3 K27M depletion increases differentiation and extends latency of diffuse intrinsic pontine glioma growth in vivo. Acta Neuropathologica. 137(4):637-655. doi: 10.1007/s00401-019-01975-4.

\item Hagiwara K., \textbf{Ding L.}, Edmonson, M.N., Rice, S.V., Newman, S., Meshinchi, S., Ries, R.E., Rusch, M., Zhang, J. (2019) RNAIndel: a machine-learning framework for discovery of somatic coding indels using tumor RNA-Seq data. bioRxiv 512749; doi: https://doi.org/10.1101/512749.

\item Xu K., \textbf{Ding L.}, Chang T.C., Shao Y., Chiang J., Mulder H., Wang S., Shaw T.I., Wen J., Hover L., McLeod C., Wang Y.D., Easton J., Rusch M., Dalton J., Downing J.R., Ellison D.W., Zhang J., Baker S.J., Wu G.. (2018) Structure and evolution of double minutes in diagnosis and relapse brain tumors. Acta Neuropathologica. 137(1):123-137. doi: 10.1007/s00401-018-1912-1.

\item Alexander T.B., Gu Z., Iacobucci I., Dickerson K., Choi J.K., Xu B., Payne-Turner D., Yoshihara H., Loh M.L., Horan J., Buldini B., Basso G., Elitzur S., de Haas V., Zwaan C.M., Yeoh A., Reinhardt D., Tomizawa D., Kiyokawa N., Lammens T., De Moerloose B., Catchpoole D., Hori H., Moorman A., Moore A.S., Hrusak O., Meshinchi S., Orgel E., Devidas M., Borowitz M., Wood B., Heerema N.A., Carrol A., Yang Y., Smith M.A., Davidsen T.M., Hermida L.C., Gesuwan P., Marra M.A., Ma Y., Mungall A.J., Moore R.A., Jones SJM., Valentine M., Janke L.J., Rubnitz J.E., Pui C., \textbf{Ding L}, Liu Y., Zhang J., Nichols K.E., Downing J.R., Cao X., Shi L., Pounds S., Newman S., Pei D., Guidry Auvil J.M., Gerhard D.S., Hunger S.P., Inaba H., Mullighan C.G.. The genetic basis and cell of origin of mixed phenotype acute leukaemia. (2018) Nature, 562(7727):373-379.

\item Mohebbi, M, \textbf{Ding, L.}, Malmberg, R.L., Momany, C, Rasheed, K, Cai, L. (2018)
Accurate prediction of human miRNA targets via graph modeling of miRNA-target duplex. Journal of Bioinformatics and Computational Biology, 7:1850013.

\item \textbf{Ding, L.}, Xue, X., LaMarca, S., Mohebbi, M., Samad, A., Malmberg, R.L., Cai, L. (2015) Accurate Prediction of RNA Nucleotide Interactions with Backbone k-Tree Model", Bioinformatics, 31(16): 2660-2667.
\end{enumerate}


\textbf{Conference Proceedings}
\begin{enumerate}
\item \textbf{Ding, L.}, Xue, X., LaMarca, S., Mohebbi M., Samad, A., Malmberg, R., and Cai, L. (2014) Abinitio prediction of RNA nucleotide interactions with backbone k-tree model", Proceedings of ECCB'14 Workshop on Computational Methods for Structural RNAs, Strasbourg France, 25-42.

\item \textbf{Ding, L.}, Samad, A., Xue, X., Huang, X., Malmberg, R., and Cai, L. (2014) Stochastic k-tree grammar and its application in bimolecular structure modeling", International Conference on Language and Automata Theory and Applications (LATA 2014) Vol 8370, 308-322.

\item \textbf{Ding, L.}, Robertson, J., Malmberg, R., and Cai, L. (2013) Protein closed loop prediction from contact probabilities", International Symposium on Bioinformatics Research and Applications (ISBRA 2013), 199-210.

\item \textbf{Ding, L.}, Fu, B., and Zhu, B. (2011) Minimum Interval Cover and Its Application to Genome Sequencing". International Conference on Combinatorial Optimization and Applications (COCOA 2011), 287- 298.

\item \textbf{Ding, L.}, Fu, B., and Fu, Y. (2010) Improved Sublinear Time Algorithm for Width- bounded Separators". International Workshop on Frontiers in Algorithmics, 101-112.

\item \textbf{Ding, L.}, Fu, B., Fu, Y., Lu, Z., and Zhao, Z. (2010) $O((log n)^2)$ Time Online Approximation Schemes for Bin Packing and Subset Sum Problem". International Workshop on Frontiers in Algorithmics, 250-261.
\end{enumerate}


\textbf{Book Chapters}
\begin{enumerate}
\item Cai, L., \textbf{Ding, L.}, Huang, X., Malmberg, RL, and Xue, X. (2014) Stochastic grammar systems for biomolecular structure modeling, Integrative Bioinformatics for Biomedical Research: A No Boundary Thinking Approach", Huang and Moore ed. Cambridge Press, to appear.

\item \textbf{Ding, L.}, Fu, B. (2013) Algebrization and Randomization Methods". Handbook of Combinatorial Optimization, Springer, pp 171-220.

\item \textbf{Ding, L.}, Fu, B., Fu, Y., Wan, Y. (2012) Application of Width-Bounded Separators to Protein Side-Chain Packing Problem", Sequence and Genome Analysis: Methods and Applications, iConcep Press.
\end{enumerate}


\textbf{Preprints}
\begin{enumerate}
\item Michael R., \textbf{Liang D.}, Sasi A., Andrew T., Hongjian J., Michael M., Lawryn K., Andre S., Michael A.D., Suzanne J.B., Jinghui Z. XenoCP: Cloud-based BAM cleansing tool for RNA and DNA from Xenograft. bioRxiv 843250; doi: https://doi.org/10.1101/843250.

\item \textbf{Ding, L.}, Chang, Di,, Malmberg, R., Martinez, A., Robinson, D., Wicker, M., Yan, H., Cai, L. (2018) Efficient Learning of Optimal Markov Network Topology with k-Tree Modeling. arXiv preprint arXiv:1801.06900.

\item \textbf{Ding. L.}, Samad, A., Xue, X., Huang, X., Cai, L. (2013) Polynomial kernels collapse the W-hierarchy. arXiv preprint arXiv:1308.3613.
\end{enumerate}
\end{rSection}

\end{document}
